\section*{Quiz 3 (Feb 7, 2020)}

\problem{
    w20q3q1
}{
    What are the 3 pipeline hazards? Which one can be solved by providing more resources?
}{
    Structural / Data / Control hazards

    Structural hazard can be solved.
}

\problem{
    w20q3q2
}{
    What are the 3 types of data hazards? Which one can be solved by using forwarding?
}{
    RAW / WAR / WAW

    RAW can be solved by forwarding.
}

\problem{
    w20q3q3
}{
    When dealing with control hazards, it is not enough to predict the branch direction, what else must we know?
}{
    Branch target address
}

\problem{
    w20q3q4
}{
    Which is on average more effective, dynamic or static branch prediction?
}{
    Dynamic
}

\problem{
    w20q3q5
}{
    \nop
}{
    a) 48

    b) No, Memory takes 2x time than the other. 
    Split M into 2 equally stages, each taking 24 time-units.
}

\problem{
    w20q3q6
}{
    \nop
}{
    \todo
}

\problem{
    w20q3q7
}{
    A simple dynamic branch prediction scheme is to use a table of 2-bit predictors, accessed using bits from the PC. 
    It would seem that the bigger the table, the better the predictor would work, is that true? 
    If not, what is the limit on how many entries the table can have and still give good perfor­mance?
}{
    False, 4096 bits.
}

\problem{
    w20q3q8
}{
    \nop
}{
    \begin{enumerate}
        \item Interrupt on \texttt{i+1} and squash the next two.
        \item Squash \texttt{i+1} to \texttt{i+5}
        \item 5, WB stage cannot go wrong.
    \end{enumerate}
}
