\section*{Quiz 5 (Feb 21, 2020)}

\problem{
    w20q5q1
    \xxxxxx
}{
    Assuming a 5-way multiple issue processor with a 9-stage pipeline and no bubbles, how many instructions are in execution at any time?
}{
    $ 5 \times 9 = 45 $
}

\problem{
    w20q5q2
    \xxxxxx
}{
    As of 2011, how many processors combine full speculation with resolving multiple branches per cycle?
}{
    No processor
}

\problem{
    w20q5q3
    \xxxxxx
}{
    Tomasulo's algorithm attempts to achieve something called Data Flow execution. 
    How does the book define Data Flow execution?
}{
    \pg{184} Operation executes as soon as their operands are available.
}

\problem{
    w20q5q4
    \xxxxxx
}{
    We have talked about two types of scheduling(static and dynamic). 
    Which type does a superscalar machine use? 
    Which one is primarily used in a VLIW machine?
}{
    VILW: static, \\
    Superscalar: both static and dynamic,
}

\problem{
    w20q5q5
    \xxxxxx
}{
    The book talks about the limits of ILP and mentions that even when using a perfect model there are some limitations. 
    What are the most important limitations that apply even to the perfect model?
}{
    \pg{220}
    \begin{enumerate}
        \item WAW \& WAR through the memory system
        \item Unnecessary dependencies
        \item Overcoming data flow limits
    \end{enumerate}
}

\problem{
    f16m2q5
    f16f0p4
    w20q5q6
}{
    Processors have been built that are able to issue 8 instructions at a time. 
    However, these pro­cessors are no longer being built - why not? 
    Why would you choose a 3-issue machine over an 8-issue machine?
}{
    Speculation requires a lot of power, and we don't get 8-issue very often because we don't always find that much parallelism, so it is not power efficient.
    I am wasting all of my energy supporting my 8-issue when I only get 3 or 4.
}

\problem{
    f12m2q15
    w20q5q7
}{
    Register renaming is used to avoid name hazards. 
    Is there a technique that can be used to minimize the number of stalls due to true (RAW) hazards? 
    If so, what is it and how does it work?
}{
    Value prediction. 
    Identify when values are being used, and using them in advance when they are needed.
}

\problem{
    w20q5q8
}{
    (Dependencies recognization \& register substitution) \\
    \nop
}{
    a)
    \begin{itemize}
        \item \RAW{1}{4}{F3}  
        \item \WAR{1}{3}{F5}      
        \item \WAR{1}{2}{F7}
        \item \WAR{1}{4}{F7}
        \item \WAR{2}{3}{F5}
        \item \RAW{2}{3}{F7}
        \item \WAW{2}{4}{F7}
        \item \WAR{3}{4}{F7}
    \end{itemize}

    b)
    15, 14, 13, 7, 11, 5, 9, 4

    c)
    \begin{itemize}
        \item \RAW{1}{4}{P7}
        \item \RAW{2}{3}{P6}
    \end{itemize}

}

\problem{
    w20q5q9
}{
    (Fine / Coarse scheduling) \\
    \nop
}{
    a)\\
        A A A   \\
        A A     \\
        B       \\
        A A     \\
        B       \\
        B B     \\

    b)\\
        A A A   \\
        B       \\
        C C     \\
        A A A   \\
        B       \\
        C       \\

    c)\\
        A A B C C \\
        A A A B C \\
        B B C C C \\
        A A B B B \\
}

