\newSection{Week 1 (Chp.1)}

\problem{
    w15f0p2
}{
    Area on the die used to be the most critical design constraint.
    That is no longer true, what is the most critical factor now? Why?
}{
    \todo
}

\problem{
    f13f0p5
    w15f0p2
    w19f0q25
}{
    What is ``leakage'' current.
    If Vdd is lowered, what happens to the amount of leakage current?
}{
    It is the current leaked when devices are off.

    Increases.
}

\problem{
}{
    In a MOS device, there is a gate, drain, and source.
    Briefly explain how this device works.
}{
    \todo
}

\problem{
    w20q1q4
}{
    Price is a key factor in the design of computers for which class?
}{
    \warn{ Embedded system. }
}

\problem{
    w20q1q10
    w20m1q16
}{
    Why are there multiple dies per silicon wafer? 
    Why not just fabricate one huge die per wafer? 
}{
    $$ \texttt{Cost of die} = \frac{\texttt{Cost of wafer}}{\texttt{Dies per wafer} \cdot \texttt{Die yield}} $$

    Making large dies lowers the yield and thus increases the cost.
}

\problem{
    w20m1q2
}{
    Is MOS technology current based or charge based.
}{
    Charge based.
}

\problem{
    w20m1q7
}{
    Which is a better metric for comparing processors, energy or power, why?
}{
    \todo
}

\problem{
    w20m1q9
}{
    What is the ``threshold voltage''
}{
    \todo
}

\problem{
    w20m1q10
}{
    Is it possible to design a flawless architecture? Explain your answer.
}{
    \todo
}

\problem{
    w20m1q11
}{
    Why do most current chips feature multiple cores on the same die?
}{
    \todo
}

\problem{
    w13f0p2
}{
    The area of the die used to be the most critical design constraint.
    That is no longer true, what is the most critical factor now? Why?
}{
    \todo
}
