\newSection{Week 10 (Chp.5, Midterm 3)}

\problem{
    w19f0q17
}{
    If I add processors but keep the job size the same, am I measuring strong or weak scaling? 
    Does this correspond most closely to response time or throughput?
}{
    Job size same, processors increase: strong scaling, response time

    Job size increase, processors increase: weak scaling, throughput
}


\problem{
    f15f0p5
}{
    What makes one instruction set harder to write a virtual machine monitor for than another one?
}{
    If instruction behaves differently when in user space and OS space, the VM can't execute directly on the hardware.
}

\problem{
    w13f0p2
    w15f0p2
    w19f0q43
}{
    What is the main difference between a commodity cluster and a custom cluster?
}{
    Different inter-connection network.
}

\problem{
    w13f0p2
    w15f0p2
    w19f0q16
}{
    There are two major c877hallenges to obtaining a substantial decrease in response time when using the MIMD approach. 
    What are they?
}{
    \begin{itemize}
        \item Communication has a long latency
        \item Finding parallelism is hard.        
    \end{itemize}
}

\problem{
    w15f0p3
    w19f0q21
}{
    Why is it difficult to come up with good benchmarks that will work across all types of parallel processors?
}{
    Because the message-passing machine and shared memory machine works differently.
    They have different algorithms, and different programming approaches.
}

\problem{
    f13f0p3
    f15f0p3
    w19f0q23
}{
    Which is harder to write a program for, a shared memory machine or a message passing machine?
    Why?
}{
    Message passing machine.
    Because you need to write the code for communication.
}

\problem{
    f13f0p3
    f15f0p3
    w19f0q24
}{
    Which is more expensive to build - a shared memory machine, or a message passing machine? 
    Why?
}{
    Shared memory machine.
    Because you need hardware to support coherent and consistent.
}

\problem{
    w13f0p3
    w15f0p1
    w19f0q44
}{
    How do two processes communicate when running on a shared memory machine?
}{
    Implicitly
}

\problem{
    f13f0p5
    w19f0q41
}{
    \info{Message passing decision, sampled from w19f0q41}

    \nop
}{
    \begin{itemize}
        \item Figure A: Shared memory
        \item Figure B: Message passing
    \end{itemize}
}


\problem{
    w15f0p2
    w19f0q18
}{
    Coherence refers to \blank is returned while consistency has to do with \blank.
    
    \OR

    Using less than 20 words explain the differences between coherence and consistency.

    \OR

    Give a one-word definition of coherence, and a one-word definition of consistency.
}{
    What, when
}