\section*{Week 1 \& 2 (1/6 - 1/19; Chp.1, Quiz 1)}

\problem{
    w15f0p2
}{
    Area on the die used to be the most critical design constraint.
    That is no longer true, what is the most critical factor now? Why?
}{
    \todo
}

\problem{
    f13f0p5
    w15f0p2
    w19f0q25
}{
    What is "leakage" current.
    If Vdd is lowered, what happends to the amount of leakage current?
}{
    It is the current leaked when devices are off.

    Increases.
}

\problem{
}{
    In a MOS device, there is a gate, drain, and source.
    Briefly explain how this device works.
}{
    \todo
}

\problem{
    w20q1q1
}{
    According to the book, in 2003 high-performance microprocessors were how many times faster than what would have been obtained by relying solely on technology?
}{
    \todo
}

\problem{
    w20q1q2
}{
    According to the book, there are two main reasons why the performance improvement of single chip processors has only been 22\% per year since 2003. What are they? 
}{
    \todo
}

\problem{
    w20q1q3
}{
    In the book they list 4 techniques that modem microprocessors use to try to improve energy effi­ciency despite flat clock rates and constant supply voltages. 
    List all of them. 
}{
    \todo
}

\problem{
    w20q1q4
}{
    Price is a key factor in the design of computers for which class?
}{
    \warn{ Embedded system. }
}

\problem{
    w20q1q6
}{
    The ISA serves as a boundary between what two things?
}{
    Programmers \& hardware
}

\problem{
    w20q1q7
}{
    Approximately how much has latency improved over the years? 
    Approximately how much has bandwidth??
}{
    \todo
}

\problem{
    w20q1q8
}{
    What is the equation for calculating dynamic power consumption?
}{
    $$ \texttt{Power} = \frac{1}{2} \cdot C \cdot V^2 \cdot f$$

    Where $C$ is the \texttt{Capative load}, $V$ is the voltage and $f$ is the frequency.
}

\problem{
    w20q1q10
    w20m1q16
}{
    Why are there multiple dies per silicon wafer? 
    Why not just fabricate one huge die per wafer? 
}{
    $$ \texttt{Cost of die} = \frac{\texttt{Cost of wafer}}{\texttt{Dies per wafer} \cdot \texttt{Die yield}} $$

    Making large dies lowers the yield and thus increases the cost.
}

\problem{
    w13f0p1
    w15f0p1
    w19f0q14
    w20q1q11
    w20m1q4
}{
    As technological advances allow us to make both transistors and wires smaller and smaller, what happens to the power density? 
}{
    The power density is higher and it will become hard to cool them down.
}

\problem{
    f13f0p3
    w15f0p2
    w19f0q26
    w20q1q12
    w20m1q17
}{
    It is difficult for the internal processing elements on a CMOS chip to cross the chip boundary and communicate with things that are on other chips. 
    Explain why that is.
}{
    The wire inside is too small, moving a little charge can transmit bits.
    Yet the wire outside is huge, there are too few electrons to transmit information.
}


\problem{
    f13f0p3
    w15f0p2
    w19f0q22
    w20m1q15
}{
    Over the years, clock rates grew by a factor of 1000 while power consumed only increased by a factor of 30. 
    How was this accomplished without melting the chip?
}{
    \warn{
        $$ \texttt{Power} = \frac{1}{2} \cdot C \cdot V^2 \cdot f$$
        Lower $V$ allows us to increase $f$ by a square to remain the same power.
    }
}

\problem{
    w20m1q1
}{
    Which has been increasing faster, latency or bandwidth?
}{
    Bandwidth
}

\problem{
    w20m1q2
}{
    Is MOS technology current based or charge based.
}{
    Charge based.
}

\problem{
    w20m1q7
}{
    Which is a better metric for comparing processors, energy or power, why?
}{
    \todo
}

\problem{
    w20m1q9
}{
    What is the "threshold voltage"
}{
    \todo
}

\problem{
    w20m1q10
}{
    Is it possible to design a flawless architecture? Explain your answer.
}{
    \todo
}

\problem{
    w20m1q11
}{
    Why do most current chips feature multiple cores on the same die?
}{
    \todo
}

\problem{
    w20m1q18
}{
    There are two different types of power consumption, static and dynamic. 
    Which one contributed the most to overall power consumption 20 years ago? 
    What is the situation now, and why has it changed?
}{
    Dynamic 20 years ago, Static nowadays.

    \todo
}

\problem{
    w13f0p2
}{
    The area of the die used to be the most critical design constraint.
    That is no longer true, what is the most critical factor now? Why?
}{
    \todo
}
